The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-27 src/ms.tex
Apply text about website and search from Jonathan
Co-authored-by: Jonathan Sick <jonathan@jsick.codes>

\item {\bf Learn Astropy website:} The website has a new search interface powered by
Algolia which is used by major e-commerce websites. This work has been
supported in part by the Dunlap grant.

>>>>

\item {\bf Learn Astropy website:} The Learn Team re-launched the website in 2021 with a new infrastructure platform, built around full-text search and interactive filtering functionality, with the goal of making content discoverable as the Learn Astropy content catalog expands.
This work has been supported in part by the Dunlap grant.
We have adopted Algolia, a search-as-a-service cloud platform, to store the full-text and metadata records of Learn Astropy's content.
The new Learn Astropy website is a JavaScript (Gatsby/React) application that uses the Algolia service to power its search and filtering user interface.
Our Python-based application, Learn Astropy Librarian, populates data into the Algolia service. We tuned the Librarian around specific content formats (such as Jupyter Notebook-based tutorial pages and Jupyter Book-based guides) to more accurately index content and heuristically extract metadata.
A consequence of the new platform is that we now maintain and compile content separately from the website application itself, enabling new content types.
Tutorials, which as Jupyter Notebook-based, are now compiled into their own Learn Astropy sub-site using nbcollection.
Guides, which are Jupyter Book-based, are also deployed as separate websites using GitHub pages. This architecture opens future possibilities of indexing third-party content, hosted elsewhere, such as on institutional websites.
